Syntactic realization with data-driven neural tree grammars

### 2016-10-10 paper/draft.tex
minor text fixes in main body; fleshing out appendix; converted talbe figures to tables

Our models predict supertags as a function of the target word and its
context.  Neural networks make it possible to generalize over such
contexts by learning to represent them with a hidden state vector that
aggregates and clusters information from the relevant history.  Our
approach is to do this using a recurrent tree network.
%
While recurrent neural networks normally use the previous hidden state in the sequential order of the inputs,
%require  the hidden state to be from the
%temporally previous hidden state,
recurrent tree networks use the hidden state from the parent.
%
Utilizing the parent's hidden state rather than the sequentially previous hidden
state, the recurrent connection can travel down the branches of a tree.
%
An example of a recurrent tree network is shown in \ref{fig:rtn}.

@@

\subsection{Results}

\begin{figure}
\centering
\begin{tabular}{|l|p{2cm}|c|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}}&\multicolumn{1}{}{} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} 
& \textbf{After A*} & Running Time \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\%  & 1.97s \\ \cline{2-5}
         &  Token       &  60.69\% & 55.56\% & 1.81s \\ \cline{2-5}
         & Minimal Token & 52.09\% & 54.18\% & 2.02s \\ \cline{2-5}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% & 0.30s \\ \cline{2-5}
         &  Token       &  82.65\% & 62.73\% & 0.36s\\ \cline{2-5}
         &  Minimal Token & 10.13\% & 19.66\% & 0.54 \\ \cline{2-5}
\hline
\end{tabular}
\label{table:accresults}
\caption{For each supertag and embedding pair, the mean accuracy of supertag classification before and after the A* algorithm is shown. Also shown is the median running time---which includes model computation and A* search.}
\end{figure}

@@

\begin{figure}
\centering
\begin{tabular}{|l|p{3cm}|p{2.5cm}|r|}
\cline{3-4}
\multicolumn{2}{}{} & \multicolumn{2}{|c|}{Accuracy}   \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Top Scoring} & \textbf{Best Performance} \\ \hline
FERGUS & n.a. & \multicolumn{2}{|c|}{74.9  \%} \\
\hline \hline
Fergus-N & Convolution & 65.80 \% & 72.58 \% \\ \cline{2-4}
         & Token       & 65.52 \%  & 71.82 \% \\ \cline{2-4}
         & Minimal Token & 63.79 \% & 71.09 \% \\ \cline{2-4}
\hline
Fergus-R & Convolution & 68.22\% & 74.70\% \\ \cline{2-4}
         & Token       &  69.29 \% & 75.56\% \\ \cline{2-4}
         & Minimal Token &  58.23 \% & 65.04\% \\ \cline{2-4}
\hline
\end{tabular}
\label{table:linresults}
\caption{Shown above as accuraccy is the percentage of tokens in the linearized strings that are in correct positions according to an edit distance measure.}
\end{figure}

@@

\section{Appendix}

\begin{figure}
\centering
\begin{tabular}{|p{6cm}|r|}
\hline
Model Parameter & Value \\ \hline
Convolution filter size & 48 \\ \hline
Optimization Algorithm & ADAM \\ \hline
Learning Rate & 0.0001 \\ \hline
Dense-Layer Dropout Rates & 0.5 \\ \hline
\end{tabular}
\label{table:params}
\caption{.}
\end{figure}

@@

>>>>

Our models predict supertags as a function of the target word and its
context.  Neural networks make it possible to generalize over such
contexts by learning to represent them with a hidden state vector that
aggregates and clusters information from the relevant history.  Our
approach is to do this using a recurrent tree network.
%
While recurrent neural networks normally use the previous hidden state in the sequential order of the inputs,
%require  the hidden state to be from the
%temporally previous hidden state,
recurrent tree networks use the hidden state from the parent.
%
Utilizing the parent's hidden state rather than the sequentially previous hidden
state, the recurrent connection can travel down the branches of a tree.
%
An example of a recurrent tree network is shown in Figure \ref{fig:rtn}.

@@

\subsection{Results}
\label{sec:results}

\begin{table}
\centering
\begin{tabular}{|l|p{2cm}|c|c|c|}
\cline{3-4}
\multicolumn{2}{}{}& \multicolumn{2}{ |c| }{ \textbf{Accuracy}}&\multicolumn{1}{}{} \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Before A*} 
& \textbf{After A*} & Running Time \\ \hline
Fergus-N &  Convolution &  58.17\% & 57.40\%  & 1.97s \\ \cline{2-5}
         &  Token       &  60.69\% & 55.56\% & 1.81s \\ \cline{2-5}
         & Minimal Token & 52.09\% & 54.18\% & 2.02s \\ \cline{2-5}
\hline
Fergus-R &  Convolution &  67.62\% & 57.04\% & 0.30s \\ \cline{2-5}
         &  Token       &  82.65\% & 62.73\% & 0.36s\\ \cline{2-5}
         &  Minimal Token & 10.13\% & 19.66\% & 0.54s \\ \cline{2-5}
\hline
\end{tabular}
\caption{For each supertag and embedding pair, the mean accuracy of supertag classification before and after the A* algorithm is shown. Also shown is the median running time---which includes model computation and A* search.}
\label{table:accresults}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{|l|p{3cm}|p{2.5cm}|r|}
\cline{3-4}
\multicolumn{2}{}{} & \multicolumn{2}{|c|}{Accuracy}   \\ \hline
\textbf{Model} & \textbf{Embedding}  & \textbf{Top Scoring} & \textbf{Best Performance} \\ \hline
FERGUS & n.a. & \multicolumn{2}{|c|}{74.9  \%} \\
\hline \hline
Fergus-N & Convolution & 65.80 \% & 72.58 \% \\ \cline{2-4}
         & Token       & 65.52 \%  & 71.82 \% \\ \cline{2-4}
         & Minimal Token & 63.79 \% & 71.09 \% \\ \cline{2-4}
\hline
Fergus-R & Convolution & 68.22\% & 74.70\% \\ \cline{2-4}
         & Token       &  69.29 \% & 75.56\% \\ \cline{2-4}
         & Minimal Token &  58.23 \% & 65.04\% \\ \cline{2-4}
\hline
\end{tabular}
\caption{Shown above as accuraccy is the percentage of tokens in the linearized strings that are in correct positions according to an edit distance measure.}
\label{table:linresults}
\end{table}

@@

\section{Appendix}
\label{sec:appendix}

\begin{table}[t!]
\centering
\begin{tabular}{lr}
\begin{tabular}[t]{|p{6cm}|r|}
\hline
\textbf{Model Parameter} & \textbf{Value} \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Fergus-N Parameters}} \\ \hline
Fully connected layer size & 256 \\ \hline
Batch size & 128 \\ \hline
\hline  \multicolumn{2}{|c|}{\textbf{Fergus-R Parameters}} \\ \hline
Fully connected layer size & 256 \\ \hline 
Hidden state size & 128 \\ \hline
Batch size & 16 \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Embedding Parameters}} \\ \hline
Convolution filter size & 48 \\ \hline
Syntactic category embedding size & 32 \\ \hline
Node role embedding size & 32 \\ \hline
Word embedding size \newline
\cite{pennington2014glove} & 300 \\ \hline
\end{tabular}
&
\begin{tabular}[t]{|p{6cm}|r|}
\hline
\textbf{Model Parameter} & \textbf{Value} \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Language Model Parameters}} \\ \hline
Hidden state size & 368 \\ \hline
Batch size & 32 \\ \hline
\hline \multicolumn{2}{|c|}{\textbf{Optimization Parameters}} \\ \hline
Optimization Algorithm & ADAM \\ \hline
Fergus-R and Fergus-N Learning Rate & 1e-4 \\ \hline
Language Model Learning Rate & 0.01 \\ \hline
Fully-Connected Dropout Rate & 0.5 \\ \hline
Recurrent Weight Dropout Rate & 0.2 \\ \hline
$L_2$ Weight Decay & 1e-6 \\ \hline
Max gradient norm & 10.0 \\ \hline
Gradient clip threshold & 5.0 \\ \hline
\end{tabular}
\end{tabular}
\caption{The parameters for the Fergus-R, Fergus-N, and language models.  The
exact specifications in configuration files can be found in the code repository that accompanies this paper.}
\label{tab:params}
\end{table}

@@

All of the models were implemented in the Keras \cite{chollet2015keras} and Theano \cite{theano} libraries.  The specific parameters that were used are shown in Table \ref{tab:params}.  The parameters were selected by measured performance on the development portion of the dataset.  In the accompanying code repository, the full experiment parameters---including progammatic parameters controlling the experimental design---are specified in configuration files.
